---
output:
  pdf_document: default
  html_document: default
---

## 02441 Applied Statistics and Statistical Software 
# Exercise 1B - Bodyfat

```{r "setup", include=FALSE}
## set working directory
require("knitr")
```

The dataset bodyfat contains measurements of bodyfat for a number of men and women 


Variable name | Description
------------- | -------------
gender | gender (male/femal)
fatpct | Measurement of fat percentage


## 1. Can the data in each group (gender) be assumed to be normally distributed

Start by loading the data (make sure datafile is present in working directory)
```{r}
# Put code here
bodyfat=read.table('bodyfat.txt', header = TRUE, sep = "")
```

Use both visual aids as well as normality tests to check the normality of fat-percentages on each gender.
```{r}
# Put code here
bodyfat_m=subset(bodyfat,bodyfat$gender=='m')
bodyfat_f=subset(bodyfat,bodyfat$gender=='f')
qqnorm(bodyfat_m$fatpct)
qqline(bodyfat_m$fatpct)
qqnorm(bodyfat_f$fatpct)
qqline(bodyfat_f$fatpct)
```

## 2. Is there a difference in the percentage of body fat for men and women? Perform a t-test
```{r }
# Put code here
t.test(bodyfat_f$fatpct,bodyfat_m$fatpct)
```

## 3. Is there a difference in the percentage of body fat for men and women? Perform a non-parametric test
```{r}
# Put code here
simx_boot <- replicate(10000, sample(bodyfat_f$fatpct, replace = TRUE))
simy_boot <- replicate(10000, sample(bodyfat_m$fatpct, replace = TRUE))
simmean_difs <- apply(simx_boot, 2, mean) - apply(simy_boot, 2, mean)
quantile(simmean_difs, c(0.025, 0.975))
```

