---
output:
  pdf_document: default
  html_document: default
---

## 02441 Applied Statistics and Statistical Software 
# Exercise 1D - laborforce


```{r "setup", include=FALSE}
## set working directory
require("knitr")
```

This dataset contains the labor force participation rate (LFPR) of women in 19 cities in the United
States in each of two years (1968 and 1972). The data help to measure the growing presence of women
in the labor force over this period.

Variable name | Description
------------- | -------------
city | City in the US
1972 | Labor Force Participation rate of women in 1972
1968 | Labor Force Participation rate of women in 1968

## 1. Compare LFPR rates in the two years with a pooled t-test since the United States did not change much from 1968 to 1972
Start by loading data:
```{r}
# Code here
labor=read.table('labor.txt', header = TRUE, sep = "")
```

If we suspect that the variance is roughly the same for the groups of 1968 and 1972 we can use a Pooled t-test in R

```{r}
# Code here
t.test(labor$x1972,labor$x1968,alternative="less",var.equal=TRUE)
```


## 2. Compare LFPR rates in the two years with a paired t-test

Paired T-test in R
```{r}
# Code here
t.test(labor$x1972,labor$x1968,paired = TRUE)
```



## 3. Which of the two methods you have used do you find most appropriate?
```{r}
# Code here
```


## 4. If you have found a significant change - how big is this change then?
```{r}
# Code here
```

