---
output:
  pdf_document: default
  html_document: default
---

## 02441 Applied Statistics and Statistical Software 
# Exercise 1C - calcium


```{r "setup", include=FALSE}
## set working directory
require("knitr")
```

Does increasing calcium intake reduce blood pressure? Observational studies suggest that there is a
link, and that it is strongest in African-American men. Twenty-one African-American men participated
in an experiment to test this hypothesis. Ten of the men took a calcium supplement for 12 weeks while
the remaining 11 men received a placebo. Researchers measured the blood pressure of each subject
before and after the 12-week period. The experiment was double-blind. The dataset calcium contains
data from the experiment.


Variable name | Description
------------- | -------------
treatment | whether subject received calcium or placebo
begin | aseated systolic blood pressure before treatment
end | aseated systolic blood pressure after treatment
decrease | decrease in blood pressure (begin-end)

## 1. What statistical test is appropriate for comparing the change in blood pressure between the treatment and placebo groups?



## 2 .May the data in each group be considered as being normally distributed?

Start by loading data:
```{r}
# put code here
calcium=read.table('calcium.txt', header = TRUE, sep = "")
```

Investigate normality
```{r}
# Put code here
qqnorm(calcium$Decrease)
qqline(calcium$Decrease)
```



## 3. Test whether the variance in each group can be assumed to be the same


```{r}
# code here
var.test(calcium_c$Decrease,calcium_p$Decrease)
```


## 4. Make a graphical comparison of the treatment means


```{r}
# Code here
calcium_c=subset(calcium,calcium$Treatment=='Calcium')
calcium_p=subset(calcium,calcium$Treatment=='Placebo')
c_c=mean(calcium_c$Decrease)
c_p=mean(calcium_p$Decrease)
plot(c_c,c_p)
```

## 5. Make the statistical test for comparing the change in blood pressure between the treatment and placebo groups. What is your conclusion? What is the p-value of the test?  


```{r}
# Code here
t.test(calcium_c$Decrease,calcium_p$Decrease)
```


## 6. Which non-parametric test could be used if data cannot be assumed to be normally distributed?

```{r}
# Code here
```
