---
output:
  pdf_document: default
  html_document: default
---

## 02441 Applied Statistics and Statistical Software 
# Exercise 1A - Climate


```{r "setup", include=FALSE}
## set working directory
require("knitr")
```


The dataset clima contains yearly average temperatures in Denmark and Greenland for the last
hundred years.  

Variable name | Description
------------- | -------------
time | Year
denmark | Average temperature in Denmark
greenland | Average temperature in Greenland

## 1. Plot the two time series and compute the correlation. What is the conclusion?

Start by loading the data (make sure datafile is present in working directory)
```{r}
# Put code here
clima=read.table('clima.txt', header = TRUE, sep = "")
```

Use the plot command in R to plot data
```{r}
# Put code here
par(mfrow=c(1,2))
plot(clima$time,clima$denmark,col='red',xlab = 'Year',ylab = 'Danmark')
plot(clima$time,clima$greenland,col='green',xlab = 'Year',ylab = 'Greenland')
```

Plot Temperatures of Greenland and Denmark up against each other to explore the relation between these two.
```{r }
# Put code here
plot(clima$denmark,clima$greenland)
```

## 2 Is the temperature in Denmark increasing when considering the time series 1900-1960? 
```{r}
# Put code here
clima_1=subset(clima,clima$time<'1961')
cor.test(clima_1$denmark,clima_1$time)
```


## 3 Is the temperature in Denmark increasing when considering the time series 1960-2000?
```{r}
# Put code here
clima_2=subset(clima,clima$time>'1960')
cor.test(clima_2$denmark,clima_2$time)
```
