---
output:
  pdf_document: default
  html_document: default
---

## 02441 Applied Statistics and Statistical Software 
# Exercise 4A - Caffeine


```{r "setup", include=FALSE}
## set working directory
require("knitr")
```

In a study the caffeine consumption by marital status among women giving birth was investigated.
The results are given in the table below

Martial-status/    Caffeine | 0  | 1-150 |  151-300 | > 300   
---- | ---- |  ---- | ---- |   ---- | 
Married | 652 | 1537 | 598 | 242
Prev. Married | 36 | 46 | 38 | 21 |
Single | 218 | 327 | 106 | 67 |

## 1. Type the data into R so that appropriate analysis can be carried out
```{r}
# Code here
caffe <- matrix(c(652,36,218,1537,46,327,598,46,106,242,21,67), ncol = 4, 
                  dimnames = list(c("Married","Prev Married",'Single'),c('0',"1-150",'151-300','>300')))
caffe
```

## 2. Determine whether Caffeine consumption and Marital status are independent
```{r}
# Code here
chisq.test(caffe,correct = FALSE)
```

## 3. If there is dependence between Caffeine consumption and Marital status, what is the conclusion?
```{r}
# COde here
mosaicplot(caffe, shade = TRUE)
```

