---
output:
  pdf_document: default
  html_document: default
---

## 02441 Applied Statistics and Statistical Software 
# Exercise 4C - Popular


```{r "setup", include=FALSE}
## set working directory
require("knitr")
```
Subjects were students in grades 4-6 from three school districts in Ingham and Clinton Counties,
Michigan. Chase and Dummer stratified their sample, selecting students from urban, suburban, and
rural school districts with approximately 1/3 of their sample coming from each district. Students
indicated whether good grades, athletic ability, or popularity was most important to them. They also
ranked four factors: grades, sports, looks, and money, in order of their importance for popularity. The
questionnaire also asked for gender, grade level, and other demographic information.

Variable name | Description
------------- | --------------------------------------------
Gender | Boy or girl
Grade | 4, 5, or 6
Age | Age in years
Race | White, Other
Urban/Rural | Rural, Suburban, or Urban school district
School | Brentwood Elementary, Brentwood Middle, Ridge, Sand, Eureka, Brown, Main Portage, Westdale Middle  
Goals |  Student's choice in the personal goals question where options were 1 = Make Good Grades 2 = Be Popular, 3 = Be Good in Sports  
Grades | Rank of "make good grades"(1=most important for popularity, 4=least important)
Sports | Rank of "being good at sports"(1=most important for popularity, 4=least important)
Looks | Rank of "being handsome or pretty"(1=most important for popularity, 4=least important)
Money | Rank of "having lots of money"(1=most important for popularity, 4=least important)

## 1. Analyze the relationship between gender and goals.
```{r}
# Code here
popular=read.table('popular.txt', header = TRUE, sep = "\t")
popular$Gender=as.factor(popular$Gender)
popular$Goals=as.factor(popular$Goals)
first=table(data.frame(popular$Gender,popular$Goals))
first
chisq.test(first)

```

## 2. Analyze the relationship between age and goals.

```{r}
#Code here
```

## 3. Could you suggest other analysis that may be interesting?

```{r}
# Code here
```

