---
output:
  pdf_document: default
  html_document: default
---

## 02441 Applied Statistics and Statistical Software 
# Exercise 4B - Diet


```{r "setup", include=FALSE}
## set working directory
require("knitr")
```
A manufacturer was considering marketing crackers high in a certain kind of edible fiber as a dieting
aid. Dieters would consume some crackers before a meal, filling their stomachs so that they would
feel less hungry and eat less. A laboratory studied whether people would in fact eat less in this way.
Female subjects ate crackers with different types of fiber (bran fiber, gum fiber, both, and a control
cracker) and were then allowed to eat as much as they wished from a prepared menu. The amount
of food they consumed and their weight were monitored, along with any side effects they reported.
Unfortunately, some subjects developed uncomfortable bloating and gastric upset from some of the
fiber crackers.

Variable name | Description
------------- | ------------------------------------
Cracker | Type of fiber in the cracker
Diet |One of four diets (type of cracker)
Subject | An identification for each of the 12 subjects
Digested | Digested calories. Difference between caloric intake and calories passed through system
Bloat | Degree of bloating and flatulence reported by the subjects

## 1. Analyze the relationship between the four types of cracker and the four levels of severity of bloating as reported by the subjects.  

```{r}
#Code here
diet=read.table('diet.txt', header = TRUE, sep = "")
diet$Cracker=as.factor(diet$Cracker)
diet$Diet=as.factor(diet$Diet)
diet$Subject=as.factor(diet$Subject)
diet$Bloat=as.factor(diet$Bloat)
str(diet)
diet1=data.frame(diet$Cracker,diet$Bloat)
str(diet1)
diet1=table(diet1)
diet1
fisher.test(diet1)
```


