---
output:
  pdf_document: default
  html_document: default
---

## 02441 Applied Statistics and Statistical Software 
# Exercise 3A - Kali


```{r "setup", include=FALSE}
## set working directory
require("knitr")
```


The dataset kali contains measurements of the content of kali (K2O) for four different productions

Variable name | Description
------------- | -------------
production | production unit
kali | content of kali


## 1. Use a non-parametric test to examine if the content of kali depends on the different productions

Start by loading and plotting the data

```{r}
# Code here
kali=read.table('kali.txt', header = TRUE, sep = "")
kali$production=as.numeric(factor(kali$production))
plot(production~kali, data = kali)
wilcox.test(kali$kali,kali$production)
```

## 2. Use a one-way ANOVA to examine if the content of kali depends on the different productions

```{r}
# Code here
str(kali)
kali$production=factor(kali$production)
str(kali)
anova(lm(kali~production,data = kali))
```

## 3. If the content of kali depends on the different productions, which of the production(s) yield the highest content?  

```{r}
# Code here
summary.lm(lm(kali~production,data = kali))
```

