
---
output:
  pdf_document: default
  html_document: default
---

## 02441 Applied Statistics and Statistical Software 
# Exercise 5B - KFM2


```{r "setup", include=FALSE}
## set working directory
require("knitr")
```
The dataset kfm contains measurements of the newborn babies, their mother and milk consumption

Variable name | Description
------------- | -------------
dl.milk | amount of breast milk (dl)
sex | gender of body
weight | baby weight (kg)
ml.suppl | amount of milk supplement (ml)
mat.weight | mothers weight (kg)
mat.height | mothers height (cm)


## 1. The purpose of this assignment is to build a model and to test predictors of the child's weight.
Of special interest is to investigate whether the effect of dl.milk, ml.suppl, mat.weight and
mat.height are different for boys and girls. Remember that the stages in model building includes
appropriate descriptive statistics, parameter estimation and testing, as well as model validation.

```{r}
# Code here
child=read.table('kfm.txt', header = TRUE, sep = "")
child$sex=factor(child$sex,labels = c(1,2))
pairs(child,col=child$sex)
step(lm(weight~.,child))
fit=lm(formula = weight ~ dl.milk + ml.suppl + mat.weight, data = child)
Anova(fit)
plot(fit)
fit2=lm(weight ~ dl.milk:sex + ml.suppl:sex + mat.weight:sex,child)
Anova(fit2)
```