---
output:
  pdf_document: default
  html_document: default
---

## 02441 Applied Statistics and Statistical Software 
# Exercise 5A - Forbes

```{r "setup", include=FALSE}
## set working directory
require("knitr")
library(car)
```

This dataset holds several facts about 77 companies selected from the Forbes 500 list for 1986. This is a
1/10 systematic sample from the alphabetical list of companies. The Forbes 500 includes all companies
in the top 500 on any of the criteria, and thus has almost 800 companies in the list. Companies are
often interested in how to increase sales.
Many of the variables are skewed { a common occurrance with financial data { which suggests that
much of the data are better analyzed after taking logarithms. For this study one should take the log
of Sales and Assets.

Variable name | Description
------------- | -------------
Company | Company Name
Assets | Amount of assets (in millions)
Sales | Amount of sales (in millions)
Market.Value | Market Value of the company (in millions)
Profits  |  Profits (in millions)
Cash.Flow | Cash Flow (in millions)
Employees | Number of employees (in thousands)
Sector | Type of market the company is associated with

## 1. Investigate the relation between Log(Sales) predicted by Log(Assets)

```{r}
# Code here
forbes=read.table('forbes.txt', header = TRUE, sep = "\t")
forbes$lSales=log(forbes$Sales)
forbes$lAssets=log(forbes$Assets)
fit=lm(lSales~lAssets,forbes)
Anova(fit)
summary(fit)
plot(fit)
```

## 2. Include Sector as a discrete factor in the model - what is your conclusion?

```{r}
# Code here
forbes$sector=factor(forbes$sector)
fit1=lm(lSales~lAssets+sector,forbes)
anova(fit1)
summary(fit1)
plot(fit1)
```

## 3. Are other variables significant?

```{r}
# Code here
forbes$Company=as.numeric(factor(forbes$Company))
Anova(lm(lAssets~.-(Assets+lSales),forbes))
```

