---
output:
  pdf_document: default
  html_document: default
---

## 02441 Applied Statistics and Statistical Software 
# Exercise 2B - Brain


```{r "setup", include=FALSE}
## set working directory
require("knitr")
```


The dataset brainweight contains measurements of the weight of both brain and body for different
mammals

Variable name | Description
------------- | -------------
art | type of mammal
body| weigth of body (kg)
brain | weight of brain (gram)


## 1. Make a scatterplot of body against brain. Do you see any correlation?

Start by loading the data

```{r}
# Code here
brain=read.table('brainweight.txt', header = TRUE, sep = "")
```

Plot body against brain
```{r}
# Code here
plot(body~brain,data = brain)
```

## 2. Make a log transform of both body and brain. Make a scatterplot of the transformed variables. Compute the correlation.

```{r}
# Code here
brain$logbody=log(brain$body)
brain$logbrain=log(brain$brain)
plot(logbody~logbrain,data = brain)
cor(brain$logbrain,brain$logbody)
```

## 3. Fit a regression model between log(body) and log(brain)

```{r}
# Code here
fit=lm(logbody~logbrain,data=brain)
summary(fit)
```

## 4. Is there any outlier in the data?  

```{r}
#Code here
par(mfrow = c(2,2))
plot(fit)


```

## 5. How would you evaluate the fit of the model?

```{r}
# Code here
plot(logbody~logbrain,data = brain)
abline(fit)
```

